Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-15 ICML-submission/from-weak-separability-to-strong-separability.tex
.

Under the weak linear separability assumption, we note that all examples from class $i$
lie in
$R_i^+ := \cap_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \ip{w_i - w_j}{x} \geq \gamma}$, and all examples from other classes lie in
$R_i^- := \cup_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \ip{w_i - w_j}{x} \leq  -\gamma}$.
Therefore, to satisfy Equations~\eqref{eqn:poly-pos-i} and~\eqref{eqn:poly-neg-i},
it suffices to construct $p_i$ such that:
\begin{align*}
  x \in R_i^+ & \Rightarrow p_i(x) \geq \frac {\gamma'} 2\\
  x \in R_i^- & \Rightarrow p_i(x) \leq - \frac {\gamma'} 2
\end{align*}

>>>>

Under the weak linear separability assumption, we note that all examples from class $i$
lie in
\[ R_i^+ := \cap_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \ip{w_i - w_j}{x} \geq \gamma}, \] and all examples from the remaining classes lie in
\[ R_i^- := \cup_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \ip{w_i - w_j}{x} \leq  -\gamma}. \]
Therefore, to satisfy Equations~\eqref{eqn:poly-pos-i} and~\eqref{eqn:poly-neg-i},
it suffices to construct $p_i$ such that:
\begin{align*}
  x \in R_i^+ & \Rightarrow p_i(x) \geq \frac {\gamma'} 2\\
  x \in R_i^- & \Rightarrow p_i(x) \leq - \frac {\gamma'} 2
\end{align*}
